---
title: "Application Exercise 15 - Communicate your results"
format: html
editor: source
editor_options: 
  chunk_output_type: console
execute:
  eval: false
---

# Exam Practice

## Task 1.0 (0.5)

1. Render the document and fix any errors.

```{r}
library(tidyverse)
```

## Task 1.1 (1)

**Fill in the blanks**

1. Use the `read_csv` function to import the following CSV file from the "data/raw_data/" directory:

- `msw-generation-and-composition-by-income.csv`, and assign to the object `waste_data`

2. Next to the code-chunk option `#| eval:` change the value from `false` to `true`

```{r}
waste_data <- ___(___)
```

## Task 1.2 (2)

**Write the code yourself**

1. Start with the `waste_data` object and use a function of your choice to create a subset that removes NAs from the variable that stores values for municipal solid waste generation.

2. Use the pipe operator to add another line of code which uses the `mutate()` function to convert the `income_cat` variable from a variable of type character to a variable of type factor. Define the factor levels yourself.

3. Store the result as a new object in your environment with the name `waste_generation_tidy` 
 
```{r}


```

## Task 1.3 (6)

**Write the code yourself**

1. Use functions taught during the course to answer the following question for the `waste_generation_tidy` data object: 

What is the minimum, mean, standard deviation, and maximum of the municipal solid waste generation grouped by income? Also add the count for the number of countries in each income category.

2. Store the result as a new object in your environment with the name `waste_generation_tbl`. 

```{r}

```

## Task 1.4 - Hand-in (0.5)

1. Render the document and fix any errors.

Last complete render: `r Sys.time()` at timezone `r Sys.timezone()`.

# Introduction

## What a Waste!

What a Waste is a global project to aggregate data on solid waste management from around the world [@world2019what].

# Results & Discussion

## Waste generation - Summary

```{r}
#| eval: false
#| echo: false

# Use functions taught during the course to answer the following question:
# Q: How many countries are covered in the data object waste_generation_tidy?


```


```{r}
#| eval: false
#| echo: false

# Use functions taught during the course to answer the following question:
# Q: How many countries are in each income category? 


```


```{r}
#| echo: false

# Include single values as inline code

```

- Data was available for ___ countries
- High income countries have an average waste generation of ___ kg/cap/year
- Low income countries have an average waste generation of ___ kg/cap/year
- Results for all income categories are shown in ___ and ___

## Waste generation - Table

```{r}
#| echo: false

waste_generation_tbl %>% 
  rename(`income category` = income_cat) %>% 
  knitr::kable(digits = 0)

```

## Waste generation - Plot

```{r}
#| echo: false

ggplot(data = waste_generation_tidy,
       mapping = aes(x = income_cat, 
                     y = msw_capita_kg_year,
                     color = income_cat)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.2) +
  scale_y_continuous(breaks = seq(0, 1600, 200)) +
  scale_color_brewer(type = "qual", palette = "Paired") +
  labs(title = "Waste generation by income category",
       x = NULL,
       y = "MSW generation per capita [kg/year]") +
  theme_minimal(base_size = 16) +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
        legend.position = "none") 

```

# References

