---
title: "Application Exercise 15 - Communicate your results"
format:
  revealjs: default
  html:
    toc: true
author:
  - name: Lars Schöbitz
  - name: Another Author
editor: source
self-contained: true
editor_options: 
  chunk_output_type: console
bibliography: 05-the-recycled.bib
execute:
  echo: true
  eval: true
  warning: false
---

# Exam Practice

## Task 1.0 (0.5)

1.  Render the document and fix any errors.

```{r}
library(tidyverse)
```

## Task 1.1 (1)

**Fill in the blanks**

1.  Use the `read_csv` function to import the following CSV file from the "data/raw_data/" directory:

-   `msw-generation-and-composition-by-income.csv`, and assign to the object `waste_data`

2.  In the YAML header, next to `eval:` change the value from `false` to `true`

```{r}
waste_data <- read_csv("data/raw_data/msw-generation-and-composition-by-income.csv")
```

## Task 1.2 (2)

**Write the code yourself**

1.  Start with the `waste_data` object and use a function of your choice to create a subset that removes NAs from the variable that stores values for municipal solid waste generation.

2.  Use the pipe operator to add another line of code which uses the `mutate()` function to convert the `income_cat` variable from a variable of type character to a variable of type factor. Define the factor levels yourself.

3.  Store the result as a new object in your environment with the name `waste_generation_tidy`

```{r}

income_cat_levels <- c("low income", "lower-middle income", "upper-middle income", "high income") 

waste_generation_tidy <- waste_data %>% 
  drop_na(msw_capita_kg_year) %>% 
  mutate(income_cat = factor(income_cat, levels = income_cat_levels)) 

```

## Task 1.3 (6)

**Write the code yourself**

1.  Use functions taught during the course to answer the following question for the `waste_generation_tidy` data object:

What is the minimum, mean, standard deviation, and maximum of the municipal solid waste generation grouped by income? Also add the count for the number of countries in each income category.

2.  Store the result as a new object in your environment with the name `waste_generation_tbl`.

```{r}

waste_generation_tbl <- waste_generation_tidy %>% 
  group_by(income_cat) %>% 
  summarise(
    count = n(),
    min = min(msw_capita_kg_year),
    mean = mean(msw_capita_kg_year),
    sd = sd(msw_capita_kg_year),
    max = max(msw_capita_kg_year)
  )
```

## Task 1.4 - Hand-in (0.5)

1.  Render the document and fix any errors.

Last complete render: `r Sys.time()` at timezone `r Sys.timezone()`.

# Introduction

## What a Waste!

What a Waste is a global project to aggregate data on solid waste management from around the world [@world2019what].

# Results & Discussion

## Waste generation - Summary

```{r}
#| eval: false
#| echo: false

# Use functions taught during the course to answer the following question:
# Q: How many countries are covered in the data object waste_generation_tidy?

waste_generation_tidy # you could read it from here, but I want the number

waste_generation_tidy %>%  # you know this way
  summarise(count = n()) 

waste_generation_tidy %>%  # another way
  nrow()
```


```{r}
#| eval: false
#| echo: false

# Use functions taught during the course to answer the following question:
# Q: How many countries are in each income category? 

waste_generation_tidy %>%  # you know this way
  group_by(income_cat) %>% 
  summarise(count = n())

waste_generation_tidy %>% # shorcut  
  count(income_cat)
```


```{r}
#| echo: false

# Include  single values as inline code

no_of_countries <- waste_generation_tidy %>%  
  summarise(count = n()) %>% 
  pull(count)

mean_waste_generation_high_income <- waste_generation_tbl %>% 
  filter(income_cat == "high income") %>% 
  pull(mean)

mean_waste_generation_low_income <- waste_generation_tbl %>% 
  filter(income_cat == "low income") %>% 
  pull(mean)

```

-   Data was available for `r no_of_countries` countries
-   High income countries have an average waste generation of `r round(mean_waste_generation_high_income)` kg/cap/year
-   Low income countries have an average waste generation of `r round(mean_waste_generation_low_income)` kg/cap/year
-   Results for all income categories are shown in @tbl-waste-generation and @fig-waste-generation

## Waste generation - Table

```{r}
#| echo: false
#| label: tbl-waste-generation
#| tbl-cap: "Waste generation by income category."

waste_generation_tbl %>% 
  rename(`income category` = income_cat) %>% 
  knitr::kable(digits = 0)

```

## Waste generation - Plot

```{r}
#| echo: false
#| label: fig-waste-generation
#| fig-cap: "Waste generation by income category."

ggplot(data = waste_generation_tidy,
       mapping = aes(x = income_cat, 
                     y = msw_capita_kg_year,
                     color = income_cat)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.2) +
  scale_y_continuous(breaks = seq(0, 1600, 200)) +
  scale_color_brewer(type = "qual", palette = "Paired") +
  labs(title = "Waste generation by income category",
       x = NULL,
       y = "MSW generation per capita [kg/year]") +
  theme_minimal(base_size = 16) +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
        legend.position = "none") 

```

# References
